\documentclass{article}
\input{item}

\title{TEST: item}
\author{KenyGeovany}
\date{11 August 2024}

\begin{document}

\maketitle

\section{Introduction}
Import item.tex with input and uses it to create an environment for biographies. 

\begin{itemize}
    \item Create items with \verb|\bioitem| command with 5 parameters: a unique label wich serves as an ID of the biography, the name, birth date and death date of the figure and a description.
    \item Print with \verb|\printBiography| command.
    \item Cite with \verb|\biohyperlink|: \biohyperlink{bioNewton}{Newton}. You can also use \verb|\hyperlink| but probably it will causes unexpected warnings \hyperlink{bioNewton}{Newton}.
    \item Cite many times do not causes error: \biohyperlink{bioWaring}{Waring1}, \biohyperlink{bioWaring}{Waring2}.
    \item If you try to cite an nonexistent bioitem then a warning message is displayed (with the corresponding line) and the link is not showed.
    \biohyperlink{bioRiemann}{Riemann}
    \item Only referenced biographies are showed. If there is not any reference to a biography then a warning message is showed. In future version a option to show all cites will be implement.
    \item All parameters for each figure need to be defined. I recommend to write \verb|?| for unknown dates.
    \item It is possible to print the pages were a biography was cited with an hyperlink?
    \item This package was tested only in overleaf.
\end{itemize}

In future versions this package will be improved.

\section{Biographies}
% Definir las biografías.
\input{biography}
% Imprimir las biografías
\printBiography


\end{document}
